Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings

### 2021-02-09 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Updated consulting slides, and high-growth MSE training

\begin{frame}
\frametitle{Targeted Training}
	High-growth businesses ("gazelles")
	\begin{itemize_2pt}
	\item
	\item
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{On-site Consulting}
	\begin{itemize_2pt}
	\item ?
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

	Consulting is intensive, tailored business advice
	\begin{itemize_2pt}
		\item Common interventions take 88 to 500 hours and more \citep{}
	\item[] $\rightarrow$ Typically 2-4 hours, between twice weekly and monthly
	\item Typical price point between \textcolor{red}{$USD$ 3,000 and 12,000 per firm} \citep{}
	\item One-on-one or group-based
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{On-site Consulting}
	\begin{itemize_2pt}
	\item Bloom, et al. (2013); Karlan et al. (2015); Bruhn, Karlan, and Schoar (2019)
	\item Large firms: \citep{Bloom2013}; SMEs: \citep{Bruhn2018}
	\item \citep{Karlan2015} \citep{Bruhn2019}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

>>>>

\begin{frame}
\frametitle{Targeted Training}
	High-growth businesses ("gazelles")
	\begin{itemize_2pt}
	\item Marcel Fafchamps and Simon Quinn
	\item Small literature on business accelerators and incubators \citep[see, e.g.,][]{Cusolito2020, Gonzalez-Uribe2017, Gonzalez-Uribe2020}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

@@

Typical Consulting Intervention
\begin{itemize_2pt}
	\item Three-step procedure
	\begin{enumerate_2pt}
		\item Diagnostic of practices
		\item Identification of areas of improvement
		\item Problem solving within interactive relationship
	\end{enumerate_2pt}

	\item \textcolor{bdf}{Sustained and intensive}
	\begin{itemize_2pt}
		\item Total of 88 to 200 hours and more \citep{Anderson2020, Bruhn2018}
		\item[] $\rightarrow$ Typically several months
		\item[] $\rightarrow$ Meetings monthly to twice weekly, 2-4 hours
		\item Total cost between \textcolor{red}{USD 4,000 and 12,000 per firm} \citep{Anderson2020, Bruhn2018}
	\end{itemize_2pt}

	\item One-on-one or group-based

	\item \textcolor{bdf}{Often gov't-subsidized} (private contributions typically around 10\%)
	\begin{itemize_2pt}
		\item Empirical finding: Firms often unwilling to pay market price \citep{Maffioli2020}
		\item[] $\rightarrow$ \textcolor{bdf}{Matching-grant programs}
	\end{itemize_2pt}

Examples in the literature
\begin{itemize_2pt}
	\item \citet{Bloom2013}; \citet{Karlan2015}; \citet{Bruhn2019}
	\item \textcolor{bdf}{Consulting in SMEs}: \citet{Bruhn2018}
	\begin{itemize_2pt}
		\item ...
		\item ...
	\end{itemize_2pt}
\end{itemize_2pt}
